The evolution of badges of status with learners

### 2019-09-05 QD_presentation.Rmd
more on the QD presentation

---
title: "The evolution of badges of status with learners"
author: "Andrés Quiñones"
bibliography: SocialMorphCue.bib
output: 
    beamer_presentation: 
      fig_caption: yes
      keep_tex: yes
header-includes: 
    \usepackage{float}
                #\floatplacement{figure}{H}
---

@@

```{r,echo=FALSE,fig.align="center",out.width='50%'}
knitr::include_graphics("Images//hawk_dove.jpeg")
```

@@

\begin{align*}
\end{align*}

```{r, echo=FALSE, out.width = '80%'}
knitr::include_graphics("Images/Hawk_dove_plot.png")
```

@@

@@

<!-- ```{r fig2, echo=FALSE, fig.cap="\\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.", out.width = '80%'} -->
<!-- knitr::include_graphics("cartoonRBF.png") -->
<!-- ``` -->

>>>>

---
title: "The evolution of badges of status with learners"
author: "Andrés Quiñones"
bibliography: SocialMorphCue.bib
output: 
    beamer_presentation: 
      fig_caption: yes
      keep_tex: yes
header-includes: 
    \usepackage{float}
    \usepackage{multicol}
    \usepackage{amsmath} 
    \usepackage{graphicx}
                #\floatplacement{figure}{H}
---

@@

```{r,echo=FALSE,fig.align="center",out.width='50%'}
knitr::include_graphics("Images//HDgame.jpeg")
```

@@

\begin{align*}
w_H &= p_H \frac{V-C}{2}+(1-p_h) V\\
w_D &= p_H 0 + (1-p_H)\frac{V}{2}
\end{align*}
\vspace{-0.8cm}
```{r, echo=FALSE,fig.align="center", out.width = '55%'}
knitr::include_graphics("Images//Hawk_dove_plot.png")
```

@@

## What about signals?

```{r,echo=FALSE,fig.align='center',out.height='80%'}
knitr::include_graphics("Images//hosp_alexandra_mackenzie.jpg")

```

## What about signals?

### When are signals honest?

* Impossible to fake
* Individuals have common interests
* Handicap principle (signal´s cost is proportional to quality)
  + Social costs?

```{r,echo=FALSE, fig.align='center',out.width='100%'}
knitr::include_graphics("Images//social_costs.png")
```

## What about signals?

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("Images//comSystemBot.png")
```

## What about learning?

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("Images//pavlov.jpg")
```

# Associative learning

## Reinforcement learning theory

\begin{columns}[T]
 \column{0.5\linewidth}
 \begin{equation*}
  \Delta V_{t(s)}=\alpha \underbrace{(R_t-V_t)}_\text{prediction error}
  \end{equation*}
  \pause
  \includegraphics[width=1\textwidth]{Images//learn_curve.png}
 \column{0.5\linewidth}
  \pause
  \includegraphics[height=.9\textheight]{Images//predErrorNeur.png}
\end{columns}

## Reinforcement learning theory

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("Images//learnUpdate.png")
```

## Environmental states

### Discrete states
\includegraphics[width=0.8\textwidth]{Images//discreteStates.png}

\pause

### Continuos states
\includegraphics[width=0.8\textwidth]{Images//contStates.png}

## Continuos environmental states

```{r fig2, echo=FALSE, fig.cap="\\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.", out.width = '80%'}
knitr::include_graphics("cartoonRBF.png")
```

@@
